---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text
    ```
    if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")
    ```
- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task

```{r}
library(RTextTools)
library(dplyr)
library(gutenbergr)
gutenberg_metadata
data("gutenbergr", package="gutenbergr")
dt<-gutenberg_works(author == "Tagore, Rabindranath")
wilde<- gutenberg_works(author=="Wilde, Oscar")
picture<- gutenberg_download(174)
gitanjali <- gutenberg_download(7164)
```

```{r}
#Data Cleaning of picture
library(tidytext)
library(stringr)
picture.chapter<- picture %>%  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("chapter [\\divxlc]",
                                                 ignore_case = TRUE))))

```

We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 

