---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text
```{r}
    if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")
```
- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 
```{r}

library(gutenbergr)
library(dplyr)
gutenberg_metadata
data("gutenbergr", package="gutenbergr")



Buddhism<- gutenberg_download(18223)
Bible<- gutenberg_download(10)
Koran<- gutenberg_download(2800)

```

```{r}
# clean data
library(tidytext)
library(ggplot2)
library(directlabels)
library(gridExtra)
library(tidyr)
library(stringr)
Bible1<-Bible %>% unnest_tokens(word, text)
Buddhism1<- Buddhism %>% unnest_tokens(word, text)
Koran1<-Koran %>% unnest_tokens(word, text)
#Analysis: The selected books are core guidance for three major religions-Christianity, Buddhism and Islam- in the world, I intend to evaluate sentiment messages conveyed in each book and make comparisons between books to see the different sentiment expressed in different religions.

#Sentiment words distribution for each book
#Get the proportion distribution table for Bible
Bible_prop<-Bible1 %>% inner_join(get_sentiments("nrc")) %>% group_by(sentiment) %>% count() %>% mutate(proportion=n/sum(n)) 
#Creat Barplot 
g1_Bi<-ggplot(Bible_prop, aes(x=sentiment,y=proportion,fill=sentiment)) + geom_bar(stat = "identity",show.legend = F)  + xlab("Sentiment Words") + ylab("Proportion") + ylim(0,0.25) + ggtitle("Sentiment words Distribution for Bible")

#Get the proportion distribution table for Buddhism                                                                 
Buddhism_prop<-Buddhism1 %>% inner_join(get_sentiments("nrc")) %>% group_by(sentiment) %>% count() %>% mutate(proportion=n/sum(n)) 
#Creat Barplot 
g1_Bu<-ggplot(Buddhism_prop,aes(x=sentiment,y=proportion,fill=sentiment)) + geom_bar(stat = "identity",show.legend = F) + xlab("Sentiment Words") + ylab("Proportion") + ylim(0,0.25) + ggtitle("Sentiment words Distribution for Buddhism")

#Get the proportion distribution table for Koran
Koran_prop<-Koran1 %>% inner_join(get_sentiments("nrc")) %>% group_by(sentiment) %>% count() %>% mutate(proportion=n/sum(n))
g1_Ko<-ggplot(Koran_prop,aes(x=sentiment,y=proportion,fill=sentiment)) + geom_bar(stat = "identity",show.legend = F) + xlab("Sentiment Words") + ylab("Proportion") + ylim(0,0.25) + ggtitle("Sentiment words Distribution for Koran")
#Combine barplots for comparison
grid.arrange(g1_Bi,g1_Bu,g1_Ko,ncol=2)
#From the comparisons of sentiment words distributions


#Find top10 positive words in each book
Bible1 %>% inner_join(get_sentiments("bing")) %>% filter(sentiment=="positive") %>% group_by(word) %>% count() %>% arrange(desc(n)) %>% top_n(10) %>% rename(frequency=n)
Buddhism1 %>% inner_join(get_sentiments("bing")) %>% filter(sentiment=="positive") %>% group_by(word) %>% count() %>% arrange(desc(n)) %>% top_n(10) %>% rename(frequency=n)
Koran1 %>% inner_join(get_sentiments("bing")) %>% filter(sentiment=="positive") %>% group_by(word) %>% count() %>% arrange(desc(n)) %>% top_n(10) %>% rename(frequency=n)
#Find most negative words in each book
Bible1 %>% inner_join(get_sentiments("bing")) %>% filter(sentiment=="negative") %>% group_by(word) %>% count() %>% arrange(desc(n)) %>% top_n(10) %>% rename(frequency=n)
Buddhism1 %>% inner_join(get_sentiments("bing")) %>% filter(sentiment=="negative") %>% group_by(word) %>% count() %>% arrange(desc(n)) %>% top_n(10) %>% rename(frequency=n)
Koran1 %>% inner_join(get_sentiments("bing")) %>% filter(sentiment=="negative") %>% group_by(word) %>% count() %>% arrange(desc(n)) %>% top_n(10) %>% rename(frequency=n)

#Find positive/negative proportions for each book
#positive/negative proportion for Bible
Bible_pn<-Bible1 %>% inner_join(get_sentiments("bing")) %>% group_by(sentiment) %>% count() %>% mutate(proportion=n/sum(n)) %>% select(sentiment,proportion)
#positive/negative proportion for Buddhism
Buddhism_pn<-Buddhism1 %>% inner_join(get_sentiments("bing")) %>% group_by(sentiment) %>% count() %>% mutate(proportion=n/sum(n)) %>% select(sentiment,proportion)
#positive/negative proportion for Buddhism
Koran_pn<-Koran1 %>% inner_join(get_sentiments("bing")) %>% group_by(sentiment) %>% count() %>% mutate(proportion=n/sum(n)) %>% select(sentiment,proportion)
#Combine all books
all_book<-inner_join(Bible_pn,Buddhism_pn,by="sentiment") %>% inner_join(Koran_pn,by="sentiment") %>% rename(Bible=proportion.x, Buddhism=proportion.y,Koran=proportion) %>% gather("book","proportion",2:4)
#Create barplot
ggplot(all_book,aes(x=book,y=proportion,fill=sentiment))+geom_bar(stat = "identity")

#Sentiment score per word for each book
Bible_score<-Bible1 %>% inner_join(get_sentiments("afinn")) %>% summarize(score_per_word=sum(score)/nrow(Bible1))
Buddhism_score<-Buddhism1 %>% inner_join(get_sentiments("afinn")) %>% summarize(score_per_word=sum(score)/nrow(Buddhism1))
Koran_score<-Koran1 %>% inner_join(get_sentiments("afinn")) %>% summarize(score_per_word=sum(score)/nrow(Koran1))
score<-rbind(Bible_score,Buddhism_score,Koran_score) %>% mutate(book=c("Bible","Buddhism","Koran"))
#Create Barplot
ggplot(score,aes(x=book,y=score_per_word,fill=book)) + geom_bar(stat = "identity", show.legend = FALSE) + xlab("Book") + ylab("Score") + ggtitle("Sentiment score per word")

#Combine all books from the group 
#CML's book
picture<- gutenberg_download(174)
picture.clean<- picture %>%  mutate(linenumber = row_number(), chapter = cumsum(str_detect(text, regex("chapter [\\divxlc]", ignore_case = TRUE)))) %>% filter(chapter >0) %>% unnest_tokens(word, text)
#Score per word for CML's book
Dorien.score<-picture.clean %>% inner_join(get_sentiments("afinn")) %>% summarize(score_per_word=sum(score)/nrow(picture.clean))
#Total score for CML's book
Dorien.score_t<-picture.clean %>% inner_join(get_sentiments("afinn")) %>% summarize(score_t=sum(score))
#Sadia's book
alice <- gutenberg_download(751)
alice_tidy<- alice %>%  
            mutate(linenumber = row_number(), chapter = cumsum(str_detect(text, regex("chapter|CHAPTER [\\divxlc]", ignore_case = TRUE)))) %>% #breaks down the book by chapter and stores the line number
  filter(chapter >0) %>% unnest_tokens(word, text)
#Score per word for Sadia's book
alice_score<-alice_tidy %>% inner_join(get_sentiments("afinn")) %>% summarize(score_per_word=sum(score)/nrow(alice_tidy))
#Total score for Sadia's book
alice_score_t<-alice_tidy %>% inner_join(get_sentiments("afinn")) %>% summarize(score_t=sum(score))
#Total scores for my books
Bible_score_t<-Bible1 %>% inner_join(get_sentiments("afinn")) %>% summarize(score_t=sum(score))
Buddhism_score_t<-Buddhism1 %>% inner_join(get_sentiments("afinn")) %>% summarize(score_t=sum(score))
Koran_score_t<-Koran1 %>% inner_join(get_sentiments("afinn")) %>% summarize(score_t=sum(score))
#Sentiment score per word for all books comparison
score_all<-rbind(Bible_score,Buddhism_score,Koran_score,Dorien.score,alice_score) %>% mutate(book=c("Bible","The Essence of Buddhism","Koran", "Picture of Dorian Gray", "Alice's Adventures in Wonderland"))
ggplot(score_all,aes(x=reorder(book,score_per_word),y=score_per_word,fill=book)) + theme_classic() + geom_bar(stat = "identity", show.legend = FALSE) + xlab("") + ylab("Score") + ggtitle("Sentiment score per word") + coord_flip()
#Total sentiment score for all books comparison
score_all_t<-rbind(Bible_score_t,Buddhism_score_t,Koran_score_t,Dorien.score_t,alice_score_t) %>% mutate(book=c("Bible","The Essence of Buddhism","Koran", "Picture of Dorian Gray", "Alice's Adventures in Wonderland"))
ggplot(score_all_t,aes(x=reorder(book,score_t),y=score_t,fill=book)) + theme_classic() + geom_bar(stat = "identity", show.legend = FALSE) + xlab("") + ylab("Score") + ggtitle("Total Sentiment score for each book") + coord_flip()

```
